---
title: "Homework 7 - S-Mobile Customer Churn"
author: 
   - name: Section 81         
   - name: Dain Hall
   - name: Trevor Cornell
output:
  html_notebook: default
---

# Preliminaries

### Determine notebook defaults:
```{r, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,      # Print all the code in all the chunks
                      warning=FALSE,  # Don't print warning statements
                      message=FALSE,  # Don't print other R output messages
                      comment=NA)     # Helps produce prettier output
```

### Load packages:
```{r, echo=FALSE, message = FALSE, warning = FALSE}
library(gmodels)
library(modelr)
library(janitor)
library(haven)
library(readxl)
library(knitr)
library(psych)
library(statar)
library(tidyverse)
library(dplyr)
library(skimr)
library(mktg482)
library(scales)
library(sjPlot)
library(nnet)
```

### Read in the data:
```{r}
# use load("filename.Rdata") for .Rdata files
load("smobile_churn.Rdata")
```

# Assignment answers

## Question 1

1. Develop a model to predict customer churn
   • Feel free to use any technique you like to predict churn
   • Make sure that one of your models is a logistic regression so that you end up
     with a set of coefficients/odds ratios for the interpretation required in step 2
   • You can use a different model for prediction and for interpretation
   • Build the model using training and test and explain your model choice or use caret with cross-validation

Hint: Don’t forget to exclude the “training,” and “customer” variables as predictors in your model.

```{r}
set.seed(1989)

smobile.train <- smobile %>% filter(training == 1) 
smobile.test <- smobile %>% filter(training == 0)

paste("Churn Rate: ", percent(mean(smobile$churn), 0.1))

# logistic regression
# Question: How to add interaction to the model?
#   * age & agemiss
#   * income & incomemiss
#   * income & profession
#   * credit rating, income, and profession
fm <- as.formula(churn ~ . - training - customer) 
lrm <- glm(fm, data=smobile.train, family=binomial)
# nnet
# nnm <- nnet(churn ~ . - training - customer, data=smobile.train, size=5, decay=0.1, maxit=1000)
# variables
varimp.logistic(lrm) %>% plotimp.logistic()

correlations <- cor(smobile.test[,1:8])
corrplot(correlations, method="circle")

smobile.test[,1:8]

```

## Question 2

Use the model to understand the main drivers of churn
• Report on the key factors that predict customer churn and their relative importance


```{r}
# smobile.test
smobile.test <- smobile.test %>% 
   mutate(pred_lr = predict(lrm, newdata=smobile.test, type="response")) %>%
   mutate(pred_nn = predict(nnm, newdata=smobile.test, type="raw")[,1]) %>%
   arrange(desc(pred_lr))


varimp.logistic(lrm) %>% 
   mutate(abs_var_imp=abs(var_imp)) %>% 
   arrange(desc(abs_var_imp)) %>% 
   select(variable, factor, abs_var_imp, var_imp) %>%
   head(10)

"
1. occhmkr1 - homemaker (stay at home mom/dad)?
2. age - of first household member
3. epqdays - age of the current phone
4. occcrft1 - occupation (crafts)
5. mou - mean monthly minutes of use
6. creditaa1 - high credit rating (aa)
7. agemiss1 - age data is missing - always include together with age variable.
8. blckvce - mean number of blocked voice calls
9. months - [-] months in service
10. occself1 - occupation - self-employed
"
gainsplot(smobile.test$pred_lr, smobile.test$pred_nn , label.var=smobile.test$churn)
```

## Question 3

Use insights to develop actions/offers/incentives
• Actions do not have to be tied to individual variables.
• Instead, consider variable groupings that make sense, e.g. “Equipment characteristic,” “Customer usage,” etc.


```{r}
"
Customer Usage [hi/low] - Higher usage, lower churn [mou, months]
Equipmentt [new/old] - Older phone, higher churn    [eqpdays]
Occupation [prof/unemp] - Unemployed, higher churn  [occhmkr, occself1, occcrft1]
Age - older, higher churn                           [age, agemiss]
Credit - better credit, lower churn                 [creditaa]
Blocked Voice - spam?                               [blckvce]
"
smobile.test
```

## Question 4

Estimate the impact of these actions/offers/incentives on the probability of churn • Either
(i) simulate the effect of a churn driver (see the hint at the end of this section) or
(ii) test the action/incentive/offer in the field
• Perform any simulation on the rollout dataset.
• Since you cannot execute a test, describe how you would set up a test and then assume a projected churn that results from the test.

*Hint:* If you want to simulate the effect of an action, do this:
• Train your model
• Create a prediction for the dataset for which for which you want to simulate variable changes (here the rollout dataset).
• Create a copy of the rollout.
• In this dataset change any variable values you want with mutate()
• For example, you want to know what giving people new phones does to attrition? Change eqpdays to a low number!
• Predict using this modified dataset.
• Compare the attrition for the groups of customers you are interested in between the original prediction and the new prediction.

```{r}
# rollout
rollout.with_prediction <- rollout %>% mutate(training=0) 

rollout.with_prediction <- rollout.with_prediction %>%
   mutate(pred_lr = predict(lrm, newdata=rollout.with_prediction, type="response")) %>%
   arrange(desc(score_lr))

paste("Predicted Churn Rate: ", percent(mean(rollout.with_prediction$churn), 0.1))

smobile.test <- smobile.test %>% 
   mutate(unemployed=occhmkr==1 || occself==1) 
smobile.test %>% filter( occself==1) %>% select(unemployed)

predict(lrm,
   newdata = smobile.test %>% filter(su_cutoff==0), type = "response") %>%
mean()

```

## Question 5

Decide which actions/offers/incentives to target to which customers
• For each action/offer/incentive specify the exact criteria to select customers.

```{r}

```

## Question 6

Evaluate the economics
• For each action/offer/incentive make the case for profitability.

```{r}

```

