---
title: "Tuango Analysis"
author:
- name: Section 81
- name: Dain Hall
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

# Preliminaries

### Determine notebook defaults:
```{r, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,      # Print all the code in all the chunks
                      warning=FALSE,  # Don't print warning statements
                      message=FALSE,  # Don't print other R output messages
                      comment=NA)     # Helps produce prettier output
```

### Load packages:
```{r, echo=FALSE, message = FALSE, warning = FALSE}
library(gmodels)
library(modelr)
library(janitor)
library(haven)
library(readxl)
library(knitr)
library(psych)
library(statar)
library(tidyverse)
library(skimr)
library(scales)
```

### Read in the data:
```{r}
# use load("filename.Rdata") for .Rdata files
# rm(list=ls())
load("/Users/dain/Programs/R_Projects/MKTG_482_HW2/Tuango_rfm.Rdata")
```

# Assignment answers

## Question 1

What percentage of customers responded (i.e. bought anything) after the push
message?

```{r}
tuango %>% filter(buyer==1) %>%
  summarise(perc_buyer=percent(n()/nrow(tuango), 0.01))
```

## Question 2

Of those who bought, what was the average spending?

(Hint: use filter(buyer==1) in the dplyr package to grab the relevant rows in the
data.)

```{r}
tuango %>% filter(buyer==1) %>%
  summarise(average_spend=dollar(mean(ordersize)))
```

## Question 3

Create (independent) quintile variables for recency, frequency and monetary. Display a table with the first six observations of the quintile variables only. 

(Hint: review the file “RFM_BBB.Rmd” which goes through the calculations for
the Bookbinders RFM analysis).

```{r}
tuango_iq <- tuango %>% 
  mutate(rec_quin_i = ntile(recency, 5), 
         freq_quin_i = ntile(-frequency, 5), 
         mon_quin_i = ntile(-monetary, 5))

tuango_iq %>% 
  select(recency, frequency, monetary, rec_quin_i, freq_quin_i, mon_quin_i) %>%
  slice(0:6)
```



## Question 4

Create bar chart showing the response rate (i.e., the proportion of customers
who bought something) to this deal by
• recency quintile
• frequency quintile
• monetary quintile
```{r}
tuango_iq %>%
  group_by(rec_quin_i) %>%
  summarize(perc_buyer = mean(buyer)) %>%
  ggplot() + geom_col(aes(x = rec_quin_i, y = perc_buyer))

tuango_iq %>%
  group_by(freq_quin_i) %>%
  summarize(perc_buyer = mean(buyer)) %>%
  ggplot() + geom_col(aes(x = freq_quin_i, y = perc_buyer))

tuango_iq %>%
  group_by(mon_quin_i) %>%
  summarize(perc_buyer = mean(buyer)) %>%
  ggplot() + geom_col(aes(x = mon_quin_i, y = perc_buyer))

```



## Question 5

Repeat questions 4 using only those customers who placed an order after the
push message, i.e. create bar charts showing the average spending (in RMB) by
recency, frequency and monetary quintile.

(Hint: use filter(buyer==1) in the dplyr package to first create a dataframe
containing only consumers who placed an order. Use that dataframe as an input
to ggplot.)

```{r}
tuango_iq %>%
  filter(buyer==1) %>%
  group_by(rec_quin_i) %>%
  summarize(avg_ordersize = mean(ordersize)) %>%
  ggplot() + geom_col(aes(x = rec_quin_i, y = avg_ordersize))

tuango_iq %>%
  filter(buyer==1) %>%
  group_by(freq_quin_i) %>%
  summarize(avg_ordersize = mean(ordersize)) %>%
  ggplot() + geom_col(aes(x = freq_quin_i, y = avg_ordersize))

tuango_iq %>%
  filter(buyer==1) %>%
  group_by(mon_quin_i) %>%
  summarize(avg_ordersize = mean(ordersize)) %>%
  ggplot() + geom_col(aes(x = mon_quin_i, y = avg_ordersize))
```


## Question 6

What do the above bar charts reveal about the likelihood of response and the
size of the order across the different recency, frequency, and monetary quintiles?

```{r}
"
The response rates of the first and second quintile of Recency & Monetary are fairly 
higher than the last 3 quintiles. The first Frequency quintile is higher, but the 
other 4 quintiles are relatively the same. It appears there is little difference 
amongst the avg ordersize quintiles, so orderise of all purchases is relatively uniform.
"
```

# Part 2

## Question 7

Create the independent RFM index in R. 

```{r}
tuango_iq <- tuango_iq %>%
  mutate(rfmindex_iq = paste(rec_quin_i, freq_quin_i, mon_quin_i, sep = '')) 

tuango_iq %>% 
  group_by(rfmindex_iq) %>% 
  summarise(perc_buyer=mean(buyer)) %>% 
  ggplot() + geom_col(aes(x = rfmindex_iq, y = perc_buyer))
```

## Question 8

Create the sequential RFM index in R.

```{r}
tuango_iq_sq <- tuango_iq %>% 
  mutate(rec_quin_s = ntile(recency, 5)) %>%
  group_by(rec_quin_s) %>% 
  mutate(freq_quin_s = ntile(-frequency, 5)) %>%
  group_by(rec_quin_s, freq_quin_s) %>% 
  mutate(mon_quin_s = ntile(-monetary, 5)) %>% 
  ungroup()

tuango_iq_sq <- tuango_iq_sq %>%
  mutate(rfmindex_sq = paste(rec_quin_s, freq_quin_s, mon_quin_s, sep = ''))  

tuango_iq_sq %>% 
  group_by(rfmindex_sq) %>% 
  summarise(perc_buyer=mean(buyer)) %>% 
  ggplot() + geom_col(aes(x = rfmindex_sq, y = perc_buyer))
```

## Question 9

Visually examine the observations in the database. What do you notice about
the independent and sequential index values? That is – do the two approaches
generally yield the same RFM index for any given customer? What do you see as
the pros and cons of the two approaches (from a statistical as well as logical
perspective) and why?

(Hint: Calculate and compare how many consumers are in each “cell” for the
independent and sequential index. You can count the number of observations
using the dplyr summarise(n()) function.)

```{r}
tuango_iq %>% 
   group_by(rfmindex_iq) %>% summarise(count=n()) %>% arrange(desc(count)) %>%
   arrange(desc(rfmindex_iq)) %>%
   slice(0:5)

tuango_iq_sq %>% 
   group_by(rfmindex_sq) %>% summarise(count=n()) %>% arrange(desc(count)) %>%
   arrange(desc(rfmindex_sq)) %>%
   slice(0:5)

"
The results are predominantly the same (the graphs are similar). Sequential method 
results are more evenly distributed customer count within each cell.˘

Sequential (Nested):
Pros:
* Even distribution of customers within each RFM cell / group
Cons:
* Assignment of customers and the results become harder to intrepet.

Independent:
Pros:
* Unambiguous assigment for 3 RFM categories. 
Cons:
* For smaller samples, may result in less even distribution of combined 
RFM scores,resulting in more empty cells.
"

```

# Part 3

## Question 10

What is the breakeven response rate?

```{r}
# Marginal Cost: 2.5RMB
# Fee per sale: 50%
# Average Order Size: ~$202

marginal_cost <- 2.5
gross_rev <- tuango %>% filter(buyer==1) %>%
  summarise(average_spend=mean(ordersize))
rev_split <- 0.5
net_rev <- gross_rev$average_spend * rev_split
response_rate <- marginal_cost / net_rev
percent(response_rate, 0.01)
```

## Question 11

What is the projected profit in RMB if you offer the deal to all remaining 264,841 customers.

```{r}
ncustomers <- 264841
marginal_cost <- 2.5
total_response_rate <- tuango_iq_sq %>% summarise(perc_buyer=mean(buyer))

dollar(ncustomers * total_response_rate$perc_buyer * net_rev - (ncustomers * marginal_cost))
```

## Question 12

Consider offering the deal only to those of the 264,841 customers in RFM cells
(using the sequential n-tiles approach) with a response rate that is equal to or
greater than the breakeven response rate.
* Calculate the response rate for the sequential quintiles approach.
* Merge the response rate back into main data.
* Calculate who you should have mailed to in your data.
* Calculate the projected profit in RMB. What is it?

(Hint: review the file “RFM_BBB.Rmd” which goes through the calculations in the
Bookbinders RFM analysis).

```{r}
resp_rate_sq_df <- tuango_iq_sq %>%
  group_by(rfmindex_sq) %>%
  summarise(resp_rate_sq=mean(buyer)) %>% 
  ungroup()

tuango_final <- tuango_iq_sq %>%
  left_join(resp_rate_sq_df)

tuango_final <- tuango_final %>%
  mutate(mailto_sq=1*(resp_rate_sq>response_rate))

targeted_customers_sq <- tuango_final %>%
  filter(mailto_sq==1) %>%
  summarise(frac_mailed=n()/nrow(tuango_final), resp_rate=mean(buyer))

# targeted_customers_sq

ntargeted_customers <- 264841 * targeted_customers_sq$frac_mailed
targeted_resp_rate <- targeted_customers_sq$resp_rate

dollar(ntargeted_customers * targeted_resp_rate * net_rev - (ntargeted_customers * marginal_cost))
```