---
title: 'PFG Bank: Credit Card Exercise'
author:
- name: Trevor Cornell
- name: Dain Hall
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

# Preliminaries

### Determine notebook defaults:
```{r, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,      # Print all the code in all the chunks
                      warning=FALSE,  # Don't print warning statements
                      message=FALSE,  # Don't print other R output messages
                      comment=NA)     # Helps produce prettier output
```

### Load packages:
```{r, echo=FALSE, message = FALSE, warning = FALSE}
library(gmodels)
library(modelr)
library(janitor)
library(haven)
library(readxl)
library(knitr)
library(psych)
library(statar)
library(tidyverse)
library(AlgDesign)
library(mktg482)
library(scales)
```

## Mailing 1

First, let's start by summarising our previous marketing campaign results.

*Note:* Throughout these steps I am retaining the same (or similar) columns so they can merged.
```{r}
# Response Rates
solicitation.results = read.csv("MKT_482_CreditCard.csv", header = TRUE)
solicitation.results
solicitation.results <- solicitation.results %>% 
   mutate(Fee=factor(Fee), APR=factor(APR)) %>%
   group_by(APR, Type, Fee) %>%
   select(APR, Type, Fee, Num_Mailed, Num_Accounts, Avg_BK) %>%
   summarise(
      Tot_Mailed=sum(Num_Mailed),
      Tot_Accounts=sum(Num_Accounts), 
      Tot_Avg_BK=weighted.mean(Avg_BK, Num_Mailed)
   ) %>% mutate(Resp_Rate=Tot_Accounts / Tot_Mailed)
solicitation.results
```

Second, we'll merge a Full Factorial design into our partial results.
```{r}
# Partial Factorial Design
solicitation.design <- list(APR=c("14.9", "16.8", "19.8"), Type=c("Fixed", "Variable"), Fee=c("20", "0")) 
solicitation.design <- expand.grid(solicitation.design)

solicitation.design <- full_join(solicitation.design, solicitation.results) %>% arrange(APR)
solicitation.design
```

Third, we'll predict what the response rate is to a solicitation for each product offer.
```{r}
lr <- glm(Resp_Rate~APR*Type*Fee, data=solicitation.design, family=binomial)

predictions <- predict(lr, newdata=solicitation.design, type="response")
solicitation.design <- solicitation.design %>% mutate(Pred_Resp_Rate = predictions) 
solicitation.design %>% select(APR, Type, Fee, Resp_Rate, Pred_Resp_Rate)
```

Fourth, we'll create a similar table of the CLV estimates that were given to us in Exhibit 2 and merge them into our analysis.
```{r}
# CLV Estimates
clv.design <- list( APR=c("14.9", "16.8", "19.8"), Type=c("Fixed", "Variable"), Fee=c("20", "0")) 
clv.full <- expand.grid(clv.design) %>% arrange(APR)
clv.results <- clv.full %>% 
   mutate(
      BK_150=c(83,93,52,62,103,113,72,82, 131,141,100,110), 
      BK_200=c(63,73,32,42,83,93,52,62,111,121,80,90),
      BK_250=c(33,43,2,12,53,63,22,32,81,91,50,60)
   ) %>% arrange(APR)
solicitation.design <- full_join(solicitation.design, clv.results)
solicitation.design %>% select(APR, Type, Fee, Pred_Resp_Rate, BK_150, BK_200, BK_250)
```

Fifth, we'll estimate the results of sending 100,000 marketing deals of each product to each CLV customer profile.

```{r}
variable_cost <- 0.50  # from Capital One ("PFG Bank"): Credit Card Exercise doc
solicitation.profit <- solicitation.design %>%
   mutate(
      BK_150_Profit=dollar((100000 * Pred_Resp_Rate * BK_150) - (100000 * variable_cost)),
      BK_200_Profit=dollar((100000 * Pred_Resp_Rate * BK_200) - (100000 * variable_cost)),
      BK_250_Profit=dollar((100000 * Pred_Resp_Rate * BK_250) - (100000 * variable_cost)),
   ) %>% select(APR, Type, Fee, Resp_Rate, Pred_Resp_Rate, BK_150, BK_200, BK_250, BK_150_Profit, BK_200_Profit, BK_250_Profit)
solicitation.profit %>% select(APR, Type, Fee, Pred_Resp_Rate, BK_150_Profit, BK_200_Profit, BK_250_Profit)
```

## Mailing 2

First, let's get the results from the first mailing into our analysis (New CSV File with added rows)
```{r}
solicitation.results2 = read.csv("MKT_482_CreditCard_v2.csv", header = TRUE)
solicitation.results2 <- solicitation.results2 %>% 
   mutate(
      Resp_Rate=Num_Accounts / Num_Mailed,
      Fee=factor(Fee), 
      APR=factor(APR)
   )

# NOTE: This time we include Avg_BK into the regression & don't group first
lr2 <- glm(Resp_Rate~APR*Type*Fee, data=solicitation.results2, family=binomial)

solicitation.results2 <- solicitation.results2 %>% 
   group_by(APR, Type, Fee) %>%
   select(APR, Type, Fee, Num_Mailed, Num_Accounts, Avg_BK) %>%
   summarise(
      Tot_Mailed=sum(Num_Mailed),
      Tot_Accounts=sum(Num_Accounts), 
      Tot_Avg_BK=weighted.mean(Avg_BK, Num_Mailed)
   ) %>% mutate(Resp_Rate=Tot_Accounts / Tot_Mailed)

# change back to column names - not sure why it wouldn't allow me to keep them as-is
colnames(solicitation.results2)[4] <- "Num_Mailed"
colnames(solicitation.results2)[5] <- "Num_Accounts"
colnames(solicitation.results2)[6] <- "Avg_BK"

# Full Design
solicitation.design2 <- list(APR=c("14.9", "16.8", "19.8"), Type=c("Fixed", "Variable"), Fee=c("20", "0")) 
solicitation.design2 <- expand.grid(solicitation.design2)

solicitation.design2 <- full_join(solicitation.design2, solicitation.results2) %>% arrange(APR)
# New Predictions - note, we don't get predictions this time because we included "BK" which is NA
predictions2 <- predict(lr2, newdata=solicitation.design2, type="response")
solicitation.design2 <- solicitation.design2 %>% mutate(Pred_Resp_Rate = predictions2) 

# CLV
solicitation.design2 <- full_join(solicitation.design2, clv.results)

# New Profit
solicitation.profit2 <- solicitation.design2 %>%
   mutate(
      BK_150_Profit=dollar((100000 * Pred_Resp_Rate * BK_150) - (100000 * variable_cost)),
      BK_200_Profit=dollar((100000 * Pred_Resp_Rate * BK_200) - (100000 * variable_cost)),
      BK_250_Profit=dollar((100000 * Pred_Resp_Rate * BK_250) - (100000 * variable_cost)),
   ) %>% select(APR, Type, Fee, Resp_Rate, Pred_Resp_Rate, BK_150, BK_200, BK_250, BK_150_Profit, BK_200_Profit, BK_250_Profit)
solicitation.profit2 %>% select(APR, Type, Fee, Pred_Resp_Rate, BK_150_Profit, BK_200_Profit, BK_250_Profit)
```


## Preparation Questions

Please see accompanying pdf 
