---
title: "ASSIGNMENT 6 - Penthalon"
author:
- Section 81
- Dain Hall
- Trevor Cornell
output:
  pdf_document: default
  html_notebook: default
---

# Preliminaries

### Determine notebook defaults:
```{r, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,      # Print all the code in all the chunks
                      warning=FALSE,  # Don't print warning statements
                      message=FALSE,  # Don't print other R output messages
                      comment=NA)     # Helps produce prettier output
```

### Load packages:
```{r, echo=FALSE, message = FALSE, warning = FALSE}
library(gmodels)
library(modelr)
library(janitor)
library(haven)
library(readxl)
library(knitr)
library(psych)
library(statar)
library(tidyverse)
library(skimr)
library(dplyr)
library(scales)
```

### Read in the data:
```{r}
# use load("filename.Rdata") for .Rdata files
load("/Users/dain/Programs/R_Projects/MKTG_482_HW6/PentathlonTargeting.RData") 

pent.nptb <- pent %>% 
   mutate(buyer=factor(buyer), female=factor(female), age=factor(age), message=factor(message)) 

```

# Assignment answers

## Part 1

### Question 1

For each customer, determine the action (a message for endurance, strength, water, team, backcountry, racquet, or the no-message control condition) that is predicted to lead to the highest probability of purchase. Describe what approach you took to predict probability of purchase.

```{r}
pent.nptb.train <- pent.nptb %>% filter(training==1) 
pent.nptb.test <- pent.nptb %>% filter(training==0)

lr.formula <- formula(buyer ~ age + female + income + education + children + freq_endurance + freq_strength + freq_water + freq_team + freq_backcountry + freq_racquet)

lr.team <- glm(lr.formula, family=binomial, data=pent.nptb.train %>% filter(message=="team"))
lr.backcountry <- glm(lr.formula, family=binomial, data=pent.nptb.train %>% filter(message=="backcountry"))
lr.endurance <- glm(lr.formula, family=binomial, data=pent.nptb.train %>% filter(message=="endurance"))
lr.water <- glm(lr.formula, family=binomial, data=pent.nptb.train %>% filter(message=="water"))
lr.racquet <- glm(lr.formula, family=binomial, data=pent.nptb.train %>% filter(message=="racquet"))
lr.strength <- glm(lr.formula, family=binomial, data=pent.nptb.train %>% filter(message=="strength"))
lr.control <- glm(lr.formula, family=binomial, data=pent.nptb.train %>% filter(message=="control"))

pent.nptb.test <- pent.nptb.test %>%
   mutate(
      pr.team = predict(lr.team, newdata=pent.nptb.test, type="response"),
      pr.backcountry = predict(lr.backcountry, newdata=pent.nptb.test, type="response"),
      pr.endurance = predict(lr.endurance, newdata=pent.nptb.test, type="response"),
      pr.water = predict(lr.water, newdata=pent.nptb.test, type="response"),
      pr.racquet = predict(lr.racquet, newdata=pent.nptb.test, type="response"),
      pr.strength = predict(lr.strength, newdata=pent.nptb.test, type="response"),
      pr.control = predict(lr.control, newdata=pent.nptb.test, type="response"),
   )

pent.nptb.test <- pent.nptb.test %>%
   mutate(
      pr.max = pmax(pr.team, pr.backcountry, pr.endurance, pr.water, pr.racquet, pr.strength, pr.control),
      pr.offer = case_when(
         pr.team == pr.max ~ "team",
         pr.backcountry == pr.max ~ "backcountry",
         pr.endurance == pr.max ~ "endurance",
         pr.water == pr.max ~ "water",
         pr.racquet == pr.max ~ "racquet",
         pr.strength == pr.max ~ "strength",
         pr.control == pr.max ~ "control",
      )
   )
pent.nptb.test %>% head(5) %>% select(custid, pr.max, pr.offer)
```

### Question 2

Report for each action the percent of customers in the test sample for whom that action maximizes their probability of purchase.


```{r}
pent.nptb.test %>% tabyl(pr.offer)
```

### Question 3

For each customer, determine the action (a message for endurance, strength, water, team, backcountry, racquet, or the no-message control condition) that is predicted to lead to the highest predicted profit (the COGS is 60%). Heads-up: There are different ways to predict order size; pick one that you think predicts order size the best. Explain how you calculated expected profit.

```{r}

osavg.team <- mean(filter(pent.nptb.test, total_os!=0 & message == "team")$total_os)
osavg.backcountry <- mean(filter(pent.nptb.test, total_os!=0 & message == "backcountry")$total_os)
osavg.endurance <- mean(filter(pent.nptb.test, total_os!=0 & message == "endurance")$total_os)
osavg.water <- mean(filter(pent.nptb.test, total_os!=0 & message == "water")$total_os)
osavg.racquet <- mean(filter(pent.nptb.test, total_os!=0 & message == "racquet")$total_os)
osavg.strength <- mean(filter(pent.nptb.test, total_os!=0 & message == "strength")$total_os)
osavg.control <- mean(filter(pent.nptb.test, total_os!=0 & message == "control")$total_os)

margin <- 0.4
pent.nptb.test <- pent.nptb.test %>%
   mutate(
      ep.team=pr.team * osavg.team * margin, 
      ep.backcountry=pr.backcountry * osavg.backcountry * margin, 
      ep.endurance=pr.endurance * osavg.endurance * margin, 
      ep.water=pr.water * osavg.water * margin, 
      ep.racquet=pr.racquet * osavg.racquet * margin, 
      ep.strength=pr.strength * osavg.strength * margin, 
      ep.control=pr.control * osavg.control * margin, 
   ) %>%
   mutate(
      ep.max = pmax(ep.team, ep.backcountry, ep.endurance, ep.water, ep.racquet, ep.strength, ep.control),
      ep.offer = case_when(
         ep.team == ep.max ~ "team",
         ep.backcountry == ep.max ~ "backcountry",
         ep.endurance == ep.max ~ "endurance",
         ep.water == ep.max ~ "water",
         ep.racquet == ep.max ~ "racquet",
         ep.strength == ep.max ~ "strength",
         ep.control == ep.max ~ "control",
      )
   )
pent.nptb.test %>% head(5) %>% select(custid, ep.max, ep.offer)
```
> Profit Formula = Predicted purchase probability * Avg Order Size for bucket * Margin
> *Predicted purchase probability:* using logistc regression and for each message
> *Avg Order size:* calculated by bucketing customers according to prior purchases.
> *Margin:* 1 - COGS %

### Question 4

Report for action the percent of customers in the test sample for whom that action maximizes their predicted profit.

```{r}
pent.nptb.test %>% tabyl(ep.offer)
```

### Question 5

Using the predicted profit for all consumers in the test sample, what profit can we obtain on average per customer when we customize the message to each customer (including potentially sending no message)?

```{r}
mean(pent.nptb.test$ep.max)
```

### Question 6

Using the predicted profit for all consumers in the test sample, what profit can Pentathlon obtain on average per customer if every customer receives the same message (or the no-message control condition)? Answer the question for each of the seven possible actions (a message for endurance, strength, water, team, backcountry, racquet, or the no-message control condition).

```{r}
pent.nptb.test %>% 
   summarise_at(vars(ep.endurance, ep.strength, ep.water, ep.team, ep.backcountry, ep.racquet, ep.control), list(mean))
```

### Question 7

Using the predicted profit for all consumers in the test sample, what profit can Pentathlon obtain on average per customer if every customer is assigned at random to receive one of the six messages?

```{r}
pent.nptb.test %>% 
   summarise_at(vars(ep.endurance, ep.strength, ep.water, ep.team, ep.backcountry, ep.racquet, ep.control), list(mean)) %>%
   rowMeans()

```

### Question 8

Based on the numbers calculated in question 5 and 6, for the typical promotional e-mail blast to 5,000,000 customer, what improvement (in percent and in total Euro) does Pentathlon expect to get from customizing the message to each customer rather than assigning customers the message that is most profitable on average?

```{r}
inc_profit <- 5000000 * mean(pent.nptb.test$ep.max) - 5000000 * mean(pent.nptb.test$ep.water)
inc_percentage <- mean(pent.nptb.test$ep.max) / mean(pent.nptb.test$ep.water) - 1

paste("Incremental Profit of ep.max v ep.water in Euros: ", dollar(inc_profit),
      "Incremental % of ep.ax v ep.water: ", percent(inc_percentage, 0.1))

```

## Part 2

Comment on the draft for a new e-mail policy proposal. Are there any weaknesses? Can you suggest at least one improvement?

> The proposed email policy is good. However, if profit margins remain constant, some customers will never receive
> different emails, missing opportunities for sales and creating poor data for future campaigns. Some amount of randomization
> and control groups should be maintained. This is a result of rerunning the same analysis monthly as opposed to randomized experiment.
> Therefore, you cannot attribute causation because the email assignments are no longer random.

Email: 

> A. Promotional e-mails will be allocated to departments on a monthly basis.
> B. For the first month after this policy goes into effect we assign customer e-mails to
>    departments as follows:
>       a. For each customer, the analytics team forecasts the actions that yield the highest
>          and the second highest expected profit among the six possible messages and
>          not sending a message.
>       b. The two departments (or no department if the control was among the two best
>          choices) who yield the highest and the second highest expected profit for a 
>          customer each control 1â„2 of the allowed e-mail messages to that customer during that month.
> C. During the last week of each subsequent month the analytics team uses the data from e-mails 
     sent during the first three weeks in that month and > repeats the analysis described in step 2.
