---
title: "Class 9: Intuit Quickbooks Upgrade: Moving to the Cloud -- Exercise"
output:
  pdf_document: default
  html_notebook: default
---

```{r, include=FALSE}
### Determine notebook defaults:
knitr::opts_chunk$set(echo=TRUE,      # Print all the code in all the chunks
                      warning=FALSE,  # Don't print warning statements
                      message=FALSE,  # Don't print other R output messages
                      comment=NA)     # Helps produce prettier output
```

```{r}
### Load packages:
# install.packages('ranger')
library(tidyverse)
library(mktg482)
library(sjPlot)
library(knitr)
library(ranger)
```

Load the data and split it into training and test:
```{r}
set.seed(2357)
load("./intuit_online.RData")
intuit.train <- intuit %>% filter(training==1)
intuit.test <- intuit %>% filter(training==0)
```

Fit a logistic regression and explore the model fit:
```{r}
rf <- ranger(res ~ state + speeddown + speedup + last + numords + dollars +
          sincepurch + version2013 + upgraded + payroll + bizflag + sex +
          income + medhvalue, data=intuit.train, probability=TRUE, mtry=3, min.node.size=1)
plot_model(rf, type="eff")
```
What do you learn about how the variables impact the prediction? Was there anything interesting or surprising?

Now, predict in the test sample:
```{r}
pred.lr.test <- predict(lr, newdata=intuit.test, type="response")
intuit.test <- intuit.test %>%
  mutate(score_lr = pred.lr.test)
```

Look at the AUC and gains of the model in the test sample:
```{r, out.width="70%", fig.align="center"}
gainsplot(intuit.test$score_lr, label.var = intuit.test$res)
```
 

If you have time, estimate the profit you would make using the logistic regression.

Hint: As usual, this requires:
1. Calculating a breakeven rate.
2. Determing what fraction you would target and their response rate.
3. Extrapolating this to 25,000 Wave 2 customers and calculating profit.
```{r}

```
 